Main Analysis for Biracial Grade Retention Project

### 2022-09-07 analysis/analysis_main.Rmd
Add rough code for new approach to figures

@@

>>>>

```{r}
marg(model4, "race", type="effects",
     at_var_interest=c("White","Black/White","Black"))
marg(model4, "race", type="effects",
     at_var_interest=c("Black","Black/Latino","Latino"))
marg(model4, "race", type="effects",
     at_var_interest=c("Asian","White/Asian"))
marg(model4, "race", type="effects",
     at_var_interest=c("Indigenous","White/Indigenous"))
marg(model4, "race", type="effects",
     at_var_interest=c("White","White/Indigenous"))
marg(model4, "race", type="effects",
     at_var_interest=c("White","White/Latino"))
marg(model4, "race", type="effects",
     at_var_interest=c("Latino","White/Latino"))
```

@@

```{r new-plot-attempt}
means_marginal <- marg(model0, "race", type="levels",
                       at_var_interest=c("White","Black/White","Black"))[[1]]

coefs <- tibble(term=str_remove(means_marginal$Label, "race = "), 
                estimate=means_marginal$Margin, 
                se=means_marginal$Standard.Error) %>%
  mutate(multiracial=str_detect(term, "/"))

coefs$estimate_mid <- ifelse(coefs$multiracial, 
                             mean(coefs$estimate[!coefs$multiracial]),
                             coefs$estimate)
coefs$se_mid <- ifelse(coefs$multiracial, 
                       sqrt(sum(coefs$se[!coefs$multiracial]^2)/4),
                       coefs$se)

coefs$ratio <- coefs$se/coefs$se[2]
coefs$ratio[2] <- coefs$se[2]/coefs$se_mid[2]

coefs$z <- 1.96*sqrt(1+coefs$ratio^2)/(1+coefs$ratio)
coefs$upper_self <- ifelse(coefs$multiracial, coefs$estimate_mid+coefs$z*coefs$se_mid,
                           coefs$estimate+coefs$z*coefs$se)
coefs$lower_self <- ifelse(coefs$multiracial, coefs$estimate_mid-coefs$z*coefs$se_mid,
                           coefs$estimate-coefs$z*coefs$se)
coefs$term <- factor(coefs$term, levels=c("White","Black/White","Black"))
coefs$colors <- ifelse(coefs$multiracial, "Multiracial", as.character(coefs$term))

se <- coefs %>%
  filter(!multiracial) %>%
  select(term, estimate, se) %>%
  rename(comparison=term, estimate_comparison=estimate, se_comparison=se)

temp <- bind_rows(coefs[2,1:3], coefs[2,1:3]) %>%
  mutate(comparison=c("Black","White")) %>%
  left_join(se) %>%
  mutate(ratio=se/se_comparison,
         z=1.96*sqrt(1+ratio^2)/(1+ratio),
         upper=ifelse(estimate<estimate_comparison, estimate+z*se, estimate),
         lower=ifelse(estimate>estimate_comparison, estimate-z*se, estimate),
         colors=comparison)

ggplot(coefs, aes(x=term, y=estimate, color=colors))+
  geom_rect(aes(xmax=Inf, xmin=-Inf, ymin=lower_self,
                ymax=upper_self, fill=colors), color=NA, alpha=0.2)+
  geom_linerange(data=temp, aes(ymin=lower, ymax=upper, color=colors),
                  position = position_dodge2(width = 0.1))+
  geom_point()+
  coord_flip()+
  scale_y_continuous(labels = scales::percent)+
  scale_color_manual(values=c("red","black","blue"))+
  scale_fill_manual(values=c("red","black","blue"))+
  labs(x=NULL,
       y="predicted probability of being behind expected grade")+
  theme_bw()+
  theme(legend.position = "none")

```
